---
title: "rvu-file-guide"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse   = FALSE,
  echo       = TRUE, 
  message    = FALSE, 
  warning    = FALSE,
  error      = TRUE,
  comment    = "#>",
  dpi        = 600, 
  out.width  = "100%",
  fig.height = 14,
  fig.width  = 10
)
options(scipen = 999)

library(rvu)
```



## Customary Charge Formula

Use the following formula for the calculation of a customary charge conversion factor:

$$
CF = \text{Customary Charge Conversion Factor} \\
CHG = \text{Physician's Customary Charge for a Procedure} \\
SVC = \text{Number of Times Physician Performed the Procedure} \\
1-n = \text{The different procedures th physician performed within a category of service} \\
RVU = \text{Relative Value Unit assigned to the procedure} \\
$$

$$
CF = \frac{ \Bigl(\frac{\text{CHG}_1}{RVU_1} \times {SVC_1}\Bigr) + \biggl(\frac{CHG_2}{RVU_2} \times {SVC_2}\biggr) + \dotsc \biggl(\frac{CHG_n}{RVU_n} \times {SVC_n}\biggr)}{ {\sum}\ SVC_{1-n} }
$$


Compute a Customary Charge Conversion Factor for a physician with the following charge history:



```{r}
(ex <- dplyr::tibble(
  procedure = 1:5,
  customary_charge = c(5, 12, 35, 20, 8),
  relative_value = c(1, 2, 4, 3, 1.5),
  frequency = c(3, 7, 5, 4, 6),
))
```
<br>

Method:
  1. For each procedure, divide the customary charge by the relative value and multiply the result by the frequency of that procedure in the physician’s charge history.
  2. Add all the results of these computations.
  3. Divide the result by the sum of all the frequencies.


```{r}
ex |> 
  dplyr::mutate(
    step = (customary_charge / relative_value) * frequency) |> 
  dplyr::summarise(
    conversion_factor = sum(step) / sum(frequency))
```



<br>

To determine a physician’s customary charge for a particular procedure where there is no reliable statistical basis, multiply the relative value of the procedure by the physician’s customary charge conversion factor for the appropriate category of service (e.g., radiology, medicine, surgery).


## Prevailing Charges

The prevailing charge conversion factors used with the appropriate relative value scale are developed from the same formula used for customary charge conversion factors, except that:

CHG $ = $ The fully adjusted locality prevailing charge for a procedure by locality and by specialty or group of specialties (regardless of the source of data from which the locality prevailing charge was developed).


SVC $ = $ The number of times the procedure was performed by all physicians in the same specialty or group of specialties and locality.


$ 1-n = $ The different procedures within a category of service for which prevailing charges have been established by specialty or group of specialties and locality.


The conversion factors calculated for any fee screen year reflect customary and prevailing charges calculated on the basis of charge data for the year ending June 30 immediately preceding the start of the fee screen year. 

Also, reasonable charge screens established through the use of a relative value scale and conversion factors consist of two components.

Consequently, the conversion factors must be recalculated when there is any change in the relative value units assigned to procedures (as may occur if you use a different or updated relative value scale) in order to assure that the change(s) in unit values do not violate the integrity of the reasonable charge screens. 

The economic index limitation, the no rollback provision, and the Administrative Savings Clause are not applied directly to prevailing charge conversion factors calculated in accordance with this section.
